### 2012-05-22 inst/examples/policycosts/stochastic_norms.Rmd
formatting

delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 50   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
sigma_m <- 0.     # noise in stock assessment measurement
sigma_i <- 0.     # noise in implementation of the quota
reward <- 0       # bonus for satisfying the boundary condition

## @knitr noise_dists
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1

@@

## @knitr profit_
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)

## @knitr create_grid_
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

## @knitr reed_sdp
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````

>>>>

delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 50   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
reward <- 0       # bonus for satisfying the boundary condition

z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1

@@

profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)

x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````
